\documentclass[12pt,fleqn,a4paper]{article}

\usepackage{latexsym}
\usepackage{url}
\usepackage{xspace}
\usepackage{epsfig}
\usepackage{psfrag}
\usepackage{a4wide}
\usepackage{marvosym}
\usepackage{amsmath,amsfonts,amssymb,amsthm,latexsym}
\usepackage{graphics,graphicx,color,subfigure}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}

\textheight 680pt
\textwidth 460pt
\topmargin -40pt
\oddsidemargin 5pt
\evensidemargin 5pt
\parindent 0pt

\pagestyle{fancyplain} \setlength{\headheight}{16pt}
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}}
\lhead[\fancyplain{}{\thepage}]
    {\fancyplain{}{\rightmark}}
\rhead[\fancyplain{}{\leftmark}]
    {\fancyplain{}{\thepage}}
\cfoot{}
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}


\begin{document}
\begin{titlepage}%Institution
\vspace{2cm}
\centerline{
\large{Department of Computer Sciences}}
\vspace{0.2cm}
\centerline{\large{University of Salzburg}}%Title with one or two Lines(More if wanted)
%\hline
\vspace{2cm}

\centerline{\large{PS Natural Computation}}
\centerline{SS 15/16}
\vspace{1cm}

\centerline{\Large{\bf{Evolution of a Poker Player Using Genetic Programming}} }%Type of the Document
\vspace{1cm}

\vspace{0.4cm}%Date
\centerline{\today}
\vspace{4.5cm}%Authors

%\hline
\vspace{0.2cm}
Project Members:\\
\centerline{Thomas Samy Dafir, 1331483, tdafir@cosy.sbg.ac.at}\\
\centerline{Laurentiu Vlad, 1423336, lvlad@cosy.sbg.ac.at}\\
\centerline{Dominik Baumgartner, 0920177, dbaumgart@cosy.sbg.ac.at}\\
\centerline{Sebastian Strumegger, 1420277, sstrumegg@cosy.sbg.ac.at}\\
\vspace {1cm}\\

Academic Supervisor: \\
\centerline{Helmut MAYER}
\centerline{helmut@cosy.sbg.ac.at}
\vspace{1.5cm}\\
Correspondence to: \\
\centerline{Universit\"{a}t Salzburg} \\
\centerline{Fachbereich Computerwissenschaften} \\
\centerline{Jakob--Haringer--Stra\ss e 2} \\
\centerline{A--5020 Salzburg} \\
\centerline{Austria}
\clearpage
\end{titlepage}

%Table of Content
\setcounter{page}{1}
\pagenumbering{Roman} %I,II,III... in the TOC
\tableofcontents

\clearpage
\pagestyle{headings}
\pagenumbering{arabic}  %Better if TOC is variable (more than one page)
\setcounter{page}{1}
\pagenumbering{arabic}  %Better if TOC is variable (more than one page)
\setcounter{page}{1}

\abstract{
The goal of this project is to evolve a GP poker player by means of genetic programming techniques.
The GP Players evolve over generations through selection, mutation and cross mutation of their chromosome tree. \\
A good computer player has to emerge after a sufficient amount of generations have been played in a "heads up" texas-hold-em no limit poker game.
Good players are determined by their fitness value which is determined through assessing a player's success after each poker round. \\
The focus of our work lies in the chromosome tree.
Although the current API provides some basics functions for that tree, it is likely that they are not sufficient for the evolution of a good player.
The second focus lies on the poker game itself.
We have to determine what kind and how much information a player needs in order to evolve properly without interfering with its evolution.
This means, that we don't want to "tell" the player what the next best action is, but rather let evolution decide.
Additionally we will do some fine-tuning of evolutionary-parameters like population size or number of generations to achieve the best possible result.
}

\newpage

\input{gp.tex}

\newpage

\input{frameworks.tex}

\newpage

% links go here, NOT in references

\section{Links}

\begin{itemize}
\item Project Page: \url{https://student.cosy.sbg.ac.at/~tdafir/nc/}
\item PS Page:
\url{http://www.cosy.sbg.ac.at/~helmut/Teaching/NaturalComputation/proseminar.html}

\end{itemize}

\nocite{*}
\bibliographystyle{ieeetr}
\bibliography{report_refs.bib}		% .bib files here

\end{document}
